Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-11 paper/main.tex
summarize discussion of AD (group) resuts

\todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
etwas}

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
categorized each frame after a cut independent of its specific content.
\todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}).
% establishing shots vs. e.g. over-the-shoulder shots
Film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that [confounding variables
could/would average out and] our whole-brain analyses would lead to significant
clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a cluster that span
the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features [or the attentional focus of study participants].
%
\todo[inline]{I am pretty surprised the clusters are not all over the brain. I
do not know where/how do phrase it but should be mentioned imo}
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas should extensively annotate the content of frames (e.g.
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus; \citep{mcnamara2017developing})[, and record the
subject's visual attention via eye-tracking].
%

\todo[inline]{concluding statements regarding exploited cinematographic
confound? e.g.: movies are nice but have idiosyncrasies? so, maybe you should be
aware of these idiosyncrasies (and control for it) in case you wanna use movies
for research?}

\todo[inline]{overall main message / concluding statement of this
``cross-modal-control-movie-thing''??}

\todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
places vs famous faces; I think they ran their f-test on the average of PPA
voxels defined by separate localizer}

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places compared
to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

>>>>

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
categorized each frame after a cut independent of its specific content.
\todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas should extensively annotate the content of frames (e.g.
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinamtography
We here took advantage of an idiosncracy of movie directing to shift from
establishing the geometry earlier in the movie to later depicting persons and
objects more relevant to the evolved plot.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in a audio-visual movie.

% intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
information embedded in the AD stimulus would correlate with increased
hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places compared
to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.
